---
title: "Part B"
author: "Wei Zhang"
date: "3/29/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(gdata)
library(dplyr)
library(lubridate)
library(ggplot2)
library(readxl)
library(chron)
```

## data cleanning

```{r}
df = read.csv("ChallengeB_Supplement_onlinelog.csv")
```

###select the school 
```{r}
data <- subset(df, orgId == 100082)
```

###status(1=enter classroom;2= exit classrroom;3=log in;4= log out)
```{r}
names(data)[5]<-"status"
```

###type(1=student;2=teacher)
```{r}
names(data)[6]<-"type"
```

```{r}
names(data)[7]<-"timestamp"
```


```{r}
data$timestamp <- as.POSIXct(data$timestamp)
```
############################################ split



###Calculate the time duration for log in and log out

###get the log in and log out observations
```{r}
data1 <- filter(data, status %in% c(3, 4))
```

```{r}
summary(data1)
```

###get the students observations
```{r}
ex <- subset(data1, type == 1 )
```

```{r}
res <- ex %>% 
  arrange(userId,timestamp) %>%
  group_by(userId) %>% 
  mutate(duration = ifelse(status > lag(status), timestamp - lag(timestamp),NA)) %>% ##Calculate time duration
  mutate(weekNum = week(timestamp))  %>% #get the week number according to time
  group_by(userId,weekNum) %>%
  mutate(durationSum = sum(duration, na.rm = TRUE))
```

## 在线时长

```{r}
head(res)
```

```{r}
daily <- ex %>% 
  arrange(userId,timestamp) %>%
  group_by(userId) %>% 
  mutate(duration = ifelse(status > lag(status), timestamp - lag(timestamp),NA)) 
  #group_by(timestamp,hournumber) %>%
  #mutate(student=n_distinct(userId))
  #mutate(time=round(timestamp,"hour"))
```

```{r}
daily$time=floor_date(daily$timestamp,"hours")
```

```{r}
daily=daily %>%
    arrange(time,userId) %>%
    group_by(time) %>%
    mutate(student=n_distinct(userId))
```

```{r}
ts_day=daily %>%
    select(time,student) %>%
    unique()
```

```{r}
time=data.frame(time=seq.POSIXt(floor_date(as.POSIXct("2018-12-01 8:00",'%m/%d/%y %H:%M')), floor_date(as.POSIXct("2019-03-17 0:00",'%m/%d/%y %H:%M')), by="hours"))
```


```{r}
ts_day2=merge(ts_day,time,all=TRUE)
ts_day2[is.na(ts_day2)]=0
```

```{r}
p=plot_ly(ts_day2,x=~time) %>%
    add_bars(y=~student) %>%
    layout(
    title = "Hourly Student Numbers",
    xaxis = list(
      rangeselector = list(
        buttons = list(
          list(
            step = "hour",
            stepmode = "backward"))),rangeslider = list(type = "date")))

chart_link = api_create(p, filename="Range")
chart_link
```

```{r}
Sys.setenv("plotly_api_key"="EK6S5pjxttogItGOPo8Y")
Sys.setenv("plotly_username"="noblegasss")
```


```{r}
length(unique(ex$userId))
```

```{r}
number=data.frame(count=c(rep("Student",66),rep("Teacher",26)))
```

```{r}
plot_ly(data=number,labels=~count,type="pie",textinfo = 'label+percent',marker=list(colors=c('rgb(128,133,133)', 'rgb(211,94,96)')))
```


## tearchers

```{r}
teachers <- subset(data1, type == 2 )

daily2 <- teachers %>% 
    arrange(userId,timestamp) %>%
    group_by(userId) %>% 
    mutate(duration = ifelse(status > lag(status), timestamp - lag(timestamp),NA)) 

daily2$time=floor_date(daily2$timestamp,"hours")

daily2=daily2 %>%
    arrange(time,userId) %>%
    group_by(time) %>%
    mutate(teacher=n_distinct(userId))

ts2_day=daily2 %>%
    select(time,teacher) %>%
    unique()

#time=data.frame(time=seq.POSIXt(floor_date(as.POSIXct("2018-12-01 8:00",'%m/%d/%y %H:%M')), floor_date(as.POSIXct("2019-03-17 0:00",'%m/%d/%y %H:%M')), by="hours"))

ts2_day2=merge(ts2_day,time,all=TRUE)
ts2_day2[is.na(ts2_day2)]=0

p=plot_ly(ts2_day2,x=~time) %>%
    add_bars(y=~teacher) %>%
    layout(
        title = "Hourly Teacher Numbers",
        xaxis = list(
            rangeselector = list(
                buttons = list(
                    list(
                        step = "hour",
                        stepmode = "backward"))),rangeslider = list(type = "date")))

chart_link = api_create(p, filename="teacher")
chart_link
```

```{r}
length(unique(teachers$userId))
```


日均上线人数
日均登陆人数

## tearchers

```{r}
daily3 <- data1 %>% 
    arrange(userId,timestamp) %>%
    group_by(userId) %>% 
    mutate(duration = ifelse(status > lag(status), timestamp - lag(timestamp),NA)) 

daily3$time=floor_date(daily3$timestamp,"hours")

daily3=daily3 %>%
    arrange(time,userId) %>%
    group_by(time) %>%
    mutate(all=n_distinct(userId))

tsall_day=daily3 %>%
    select(time,all) %>%
    unique()

#time=data.frame(time=seq.POSIXt(floor_date(as.POSIXct("2018-12-01 8:00",'%m/%d/%y %H:%M')), floor_date(as.POSIXct("2019-03-17 0:00",'%m/%d/%y %H:%M')), by="hours"))

tsall_day2=merge(tsall_day,time,all=TRUE)
tsall_day2[is.na(tsall_day2)]=0

p=plot_ly(tsall_day2,x=~time) %>%
    add_bars(y=~all) %>%
    layout(
        title = "Hourly Numbers",
        xaxis = list(
            rangeselector = list(
                buttons = list(
                    list(
                        step = "hour",
                        stepmode = "backward"))),rangeslider = list(type = "date")))

chart_link = api_create(p, filename="all")
chart_link
```


## Vital Signs

```{r}
day4=day3
day4$time=as.factor(day4$time)
```


```{r}
ggpairs(day3[,c(1,2,3)],aes(alpha=0.75), lower=list(continuous="smooth"))+ theme_bw()+
labs(title="Correlation Plot")+
theme(plot.title=element_text(face='bold',color='black',hjust=0.5,size=12))
```

```{r}
corrplot::corrplot(day3)
```


```{r}
day3=day_2
day3$time=c(1:97)
```


```{r}
poi=glm(usernum~time,data=day3,family=poisson(link="log"))
poi2=glm(usernum~weekNum,data=weekly_2,family=poisson(link="log"))
```

```{r}
summary(poi)
summary(poi2)
```

```{r}
plot(poi)
plot(poi2)
```


```{r}
predict(poi2,type="response")
```

```{r}
poi3=glm(logintimes~time,data=day3,family=poisson(link="log"))
```

```{r}
summary(poi3)
```

```{r}
ts1=ts(data=day3$usernum,frequency=365,start = c(2018,12))
ts2=ts(data = week2$usernum,frequency=52,start = c(2018,12))
```

```{r}
ts1.mo=auto.arima(ts1)
```
```{r}
ts2.mo=auto.arima(ts2)
```


```{r}
summary(ts1.mo)
```

```{r}
ts3=ts(data=day3$logintimes,frequency=365,start = c(2018,12))
ts3.mo=auto.arima(ts3)
```

```{r}
summary(ts3.mo)
```


```{r}
ts1.mo %>%
  forecast(h=3) %>%
  autoplot() +
    ylab("Login") +  xlab("Time")
```

```{r}
ts3.mo %>%
  forecast(h=3) %>%
  autoplot() +
    ylab("Users") +  xlab("Time")
```


```{r}
ggplot(dat=day3, aes(time, logintimes)) + 
      geom_point() +
      geom_smooth(method="glm", method.args=list(family="poisson"), 
                  fullrange=TRUE, se=TRUE) +
      xlim(0, 100)
```

```{r}

```



```{r}
ts2.mo %>%
  forecast(h=2) %>%
  autoplot() +
    ylab("Users") +  xlab("Time")
```

```{r}
ggplot(dat=day3, aes(time, usernum)) + 
      geom_point() +
      geom_smooth(method="glm", method.args=list(family="poisson"), 
                  fullrange=TRUE, se=TRUE) +
      xlim(0, 100)
```

```{r}
d <- data.frame(time=0:100)
pred=predict(poi,d,type="response")
f=data.frame(time=0:100,pre=pred)
```

```{r}
plot_ly() %>%
    add_trace(data=d,x=~time,y=~pred,add=TRUE,name="Predict") %>%
    add_trace(data=day3,y=~usernum,x=~time,name="Ture Value")
```


```{r}
d=data.frame(time=0:100,pred=pred)
ggplot() + 
  # prediction line
  geom_line(data=f, aes(time, pred),color="red") +
  # points - note different dataframe is used
  geom_point(dat=day3, aes(time, usernum))
```

```{r}
pred2=predict()
```



```{r}
e <- data.frame(weekNum=0:20)
pred2=predict(poi2,e,type="response")
```

```{r}
ggplot(dat=week2, aes(weekNum, logintimes)) + 
      geom_point() +
      geom_smooth(method="glm", method.args=list(family="poisson"), 
                  fullrange=TRUE, se=TRUE) +
      xlim(0, 20)
```


```{r}
ggplot(dat=week2, aes(weekNum, usernum)) + 
      geom_point() +
      geom_smooth(method="glm", method.args=list(family="poisson"), 
                  fullrange=TRUE, se=TRUE) +
      xlim(0, 20)
```


## Negative Binomial Regression

```{r}
nb=glm.nb(usernum~time,data=day3)
```

```{r}
summary(nb)
```

```{r}
pred3=predict(nb,d,type="response")
res=data.frame(time=d,pre=pred3)
```

```{r}
plot_ly() %>%
    add_trace(data=res,x=~time,y=~pred3,add=TRUE,name="Predict") %>%
    add_trace(data=day3,y=~usernum,x=~time,name="Ture Value")
```


```{r}
nb2=glm.nb(logintimes~time,data=day3)
pred4=predict(nb,d,type="response")
re2=data.frame(time=d,pre=pred4)
```

```{r}
plot_ly() %>%
    add_trace(data=re2,x=~time,y=~pred4,add=TRUE,name="Predict") %>%
    add_trace(data=day3,y=~logintimes,x=~time,name="Ture Value")
```


```{r}
nb3=glm.nb(usernum~weekNum,data=week2)
nb4=glm.nb(logintimes~weekNum,data=week2)
```

```{r}
pred5=predict(nb3,e,type="response")
re3=data.frame(time=e,pre=pred5)
```

```{r}
plot_ly() %>%
    add_trace(data=re3,x=~weekNum,y=~pred5,add=TRUE,name="Predict") %>%
    add_trace(data=week2,y=~usernum,x=~weekNum,name="Ture Value")
```

```{r}
pred6=predict(nb4,e,type="response")
re4=data.frame(time=e,pre=pred6)
```

```{r}
plot_ly() %>%
    add_trace(data=re4,x=~weekNum,y=~pred6,add=TRUE,name="Predict") %>%
    add_trace(data=week2,y=~logintimes,x=~weekNum,name="Ture Value")
```

## active

```{r}
week=data1 %>%
    arrange(timestamp) %>%
    mutate(weekNum = week(timestamp))  %>% 
    filter(status==3) %>%
    group_by(weekNum) %>%
    mutate(logintimes=length(userId)) %>%
    mutate(usernum=n_distinct(userId)) %>%
    mutate(avglogin=logintimes/usernum)
    
summary(week)
```



```{r}
week2=week %>%
    select(weekNum,logintimes,usernum,avglogin) %>%
    unique()
```

```{r}
week2=week2[c(1:18),]
week2$weekNum=c(1:18)
```


```{r}
summary(week2)
```

```{r}
plot_ly(week2,x=~weekNum) %>%
    add_bars(y=~logintimes,name="Login",color="red") %>%
    add_bars(y=~usernum,name="Users",color="green") %>%
    add_bars(y=~avglogin,name="Weekly Average",color="orange")
```


teacher：26
student：66
total：92

active: 周login次数>7

```{r}
weekactive=week %>%
    group_by(weekNum,userId) %>%
    mutate(active = ifelse(length(id)>=3, 1,0)) %>%
    select(weekNum,userId,active) %>%
    unique() %>%
    group_by(weekNum) %>%
    mutate(total=length(userId)) %>%
    filter(active==1) %>%
    mutate(activenumber=length(userId)) %>%
    select(weekNum,activenumber,total) %>%
    unique() %>%
    mutate(nonactive=total-activenumber)
```

```{r}
weekactive$weekNum=c(1:18)
summary(weekactive)
```

```{r}
plot_ly(weekactive,x=~weekNum,mode="line") %>%
    add_trace(y=~activenumber,name="Active",color="red") %>%
    add_trace(y=~total,name="Total",color="blue")
```

```{r}
data2=data1

data2$time=floor_date(data2$timestamp,"hours")

data2=data2 %>%
    arrange(time,userId) %>%
    group_by(time) %>%
    mutate(all=n_distinct(userId)) %>%
    mutate(numbers=length(userId))

tslog_day=data2 %>%
    select(time,all,numbers) %>%
    unique()

tslog_day2=merge(tslog_day,time,all=TRUE)
tslog_day2[is.na(tslog_day2)]=0
```

```{r}
a=plot_ly(tslog_day2,x=~time) %>%
    add_bars(y=~numbers,name="Login") %>%
    add_bars(y=~all,name="Users") %>%
    layout(
        title = "Hourly Logins and Users Numbers",
        xaxis = list(
            rangeselector = list(
                buttons = list(
                    list(
                        step = "hour",
                        stepmode = "backward"))),rangeslider = list(type = "date")))
    
chart_link = api_create(a, filename="login")
chart_link
```

## daily

```{r}

day=data1
day$time=floor_date(day$timestamp,"days")

day=day %>%
    filter(status==3) %>%
    group_by(time) %>%
    mutate(logintimes=length(userId)) %>%
    mutate(usernum=n_distinct(userId))
    
summary(day)
```

```{r}
day_2=day %>%
    select(time,logintimes,usernum) %>%
    unique()
```


```{r}
time2=data.frame(time=seq.POSIXt(floor_date(as.POSIXct("2018-11-30",'%m/%d/%y')), floor_date(as.POSIXct("2019-03-17",'%m/%d/%y')), by="day"))
```

```{r}
day2=merge(day_2,time2,by="time",all=TRUE)
#day2[is.na(day2)]=0
```

```{r}
b=plot_ly(day_2,x=~time) %>%
    add_bars(y=~logintimes,name="Login") %>%
    add_bars(y=~usernum,name="Users") %>%
    layout(
        title = "Daily Logins and Users Numbers",
        xaxis = list(
            rangeselector = list(
                buttons = list(
                    list(
                        step = "day",
                        stepmode = "backward"))),rangeslider = list(type = "date")))
    
chart_link = api_create(b, filename="dailylogin")
chart_link
```


## weekly

```{r}
weekly=data1

weekly=weekly %>%
    mutate(weekNum = week(timestamp))  %>% 
    filter(status==3) %>%
    group_by(weekNum) %>%
    mutate(logintimes=length(userId)) %>%
    mutate(usernum=n_distinct(userId))
    
summary(weekly)
```

```{r}
weekly_2=weekly %>%
    select(weekNum,logintimes,usernum) %>%
    unique()
```

```{r}
weekly_2$weekNum=c(1:19)
```



```{r}
summary(weekly_2)
```

```{r}
c=plot_ly(weekly_2,x=~weekNum) %>%
    add_bars(y=~logintimes,name="Login") %>%
    add_bars(y=~usernum,name="Users") %>%
    layout(
        title = "Weekly Logins and Users Numbers",
        xaxis = list(
            rangeselector = list(
                buttons = list(
                    list(
                        step = "week",
                        stepmode = "backward"))),rangeslider = list(type = "date")))
    
chart_link = api_create(c, filename="weeklylogin")
chart_link
```


## 月均活跃度

```{r}
month=data1 %>%
    arrange(timestamp) %>%
    mutate(month = month(timestamp))  %>% 
    filter(status==3) %>%
    group_by(month) %>%
    mutate(logintimes=length(userId)) %>%
    mutate(usernum=n_distinct(userId))
```

```{r}
summary(month)
```



```{r}
monthactive=month %>%
    group_by(month,userId) %>%
    mutate(active = ifelse(length(id)>=18, 1,0)) %>%
    select(month,userId,active) %>%
    unique() %>%
    group_by(month) %>%
    mutate(total=length(userId)) %>%
    filter(active==1) %>%
    mutate(activenumber=length(userId)) %>%
    select(month,activenumber,total) %>%
    unique() %>%
    mutate(nonactive=total-activenumber)
```

```{r}
summary(monthactive)
```

```{r}
monthactive$month=c("Nov","Dec","Jan","Feb","Mar")
monthactive$month=factor(monthactive$month,levels=c("Nov","Dec","Jan","Feb","Mar"))
```


```{r}
plot_ly(monthactive,x=~month,mode="line") %>%
    add_lines(y=~activenumber,name="Active",color="red") %>%
    add_lines(y=~total,name="Total",color="blue")
```

```{r}
data2=data1

data2$time=floor_date(data2$timestamp,"hours")

data2=data2 %>%
    arrange(time,userId) %>%
    group_by(time) %>%
    mutate(all=n_distinct(userId)) %>%
    mutate(numbers=length(userId))

tslog_day=data2 %>%
    select(time,all,numbers) %>%
    unique()

tslog_day2=merge(tslog_day,time,all=TRUE)
tslog_day2[is.na(tslog_day2)]=0
```

```{r}
a=plot_ly(tslog_day2,x=~time) %>%
    add_bars(y=~numbers,name="Login") %>%
    add_bars(y=~all,name="Users") %>%
    layout(
        title = "Hourly Logins and Users Numbers",
        xaxis = list(
            rangeselector = list(
                buttons = list(
                    list(
                        step = "hour",
                        stepmode = "backward"))),rangeslider = list(type = "date")))
    
chart_link = api_create(a, filename="login")
chart_link
```


## 人均停留时间

